---
title: "Alcohol–related Hospital Admissions"
output: 
  flexdashboard::flex_dashboard:
    logo: ../phs_logo_mono.png
    orientation: rows
    vertical_layout: scroll
    css: www/css_styles.css
params:
  qtr_start:
    value: "default"
  qtr_end:
    value: "default"
---



```{r setup, include=FALSE}
library(here)
library(htmltools)
library(tidyverse)
library(knitr)
library(lubridate)
library(reactable)
library(sparklines)
library(phsstyles)
library(plotly)
library(downloadthis)

knitr::opts_chunk$set(echo = FALSE)

if ("default" %in% params){
  stop("You must provide the knitting of this .Rmd with the parameters: qtr_start, qtr_end")
}

data_dir <- here("output", "admissions_qtr_data", "accumulated", paste0("qtr_alc_adm_GGC_", params$qtr_start, "_to_", params$qtr_end, ".csv"))
data <- read_csv(data_dir) %>% 
  select(-lookup) %>% 
  mutate(date_end = ymd(date_end),
         area=recode(area, `NHS Greater Glasgow and Clyde`="NHS GGC"))

source(here("dashboard", "funcs_wrangle.R"))
source(here("dashboard", "funcs_dashboard.R"))
source(here("dashboard", "qtr_report", "process_wrangle_qtr_roc.R"))
source(here("dashboard", "qtr_report", "table_output_qtr.R"))

big_areas <- c("Scotland", "NHS Greater Glasgow and Clyde", "NHS GGC")

p_m_colours <- make_p_m_color_pal(c("#d26146", "#9cc951", "#ffffff"), bias=1.5)
```

Notes {data-icon="fa-info-circle"}
===================================== 

row
--------------------------------------------------

###

#### **Alcohol-Related Hospital Admissions**
#### **NHS Greater Glasgow and Clyde**
##### Report date: `r format(Sys.time(), "%d %b %Y")`

<br/>

This report contains

- Trends in EASR (per 10,000 population) and Number of Admissions.
- Percentage change in EASR and Number of Admissions (from first year and year-on-year).
- Figures shown are for one-year time periods on a rolling quarterly basis.

EASR - European Age-Sex Standardised Rate

<br/>

#### <span style="text-decoration:underline">**Data Notes**</span>


(1) Alcohol-related hospital admissions
Source: SMR01, Public Health Scotland

- The number of inpatient and day case stays where an alcohol-related condition is recorded in any of the 6 diagnostic positions.
- Alcohol-related condition ICD-10 diagnosis codes: E24.4, E51.2, F10, G31.2, G62.1, G72.1, I42.6, K29.2, K70, K85.2, K86.0, O35.4, P04.3, Q86.0, R78.0, T51.0, T51.1, T51.9, X45, X65, Y15, Y57.3, Y90, Y91, Z50.2, Z71.4, Z72.1.
- Includes both elective and non-elective admissions.

(2) Population Estimates
Source: Mid-Year Population Estimates, National Records Scotland




Admission Trends {data-icon="fa-table"}
===================================== 

Info {.sidebar}
-------------------------------------

**Alcohol-related hospital admissions**

**NHS Greater Glasgow and Clyde and HSCPs.**


- Trends in EASR (per 10,000 population) and Number of Admissions 
- In the table choose between the tabs to show either EASR or Number of admissions.
- A summary trend is shown at the end of each row of the table. 
- The chart below the table shows the trend in EASR in more detail. Click on the traces in the legend of the chart to show/hide them.
- If viewed on a narrow screen, press shift while scrolling on the mouse and hovering over the table to scroll the table horizontally.



row {.tabset data-height=390}
--------------------------------------------------

### EASR

```{r reactable_2}
trend_table_data_2 <- format_and_pivot(data, "EASR")

trend_table_data_2 %>% 
  download_this(
    output_name = "EASR trends",
    output_extension = ".xlsx",
    button_label = "Download Data",
    button_type = "primary",
    has_icon = TRUE,
    icon = "fa fa-save",
    csv2 = FALSE
  )

table_with_sparklines(trend_table_data_2, n_digits = 1)

```

### Number
```{r reactable_1}
trend_table_data_1 <- format_and_pivot(data, "number")

trend_table_data_1 %>% 
  download_this(
    output_name = "Number trends",
    output_extension = ".xlsx",
    button_label = "Download Data",
    button_type = "primary",
    has_icon = TRUE,
    icon = "fa fa-save",
    csv2 = FALSE
  )

table_with_sparklines(trend_table_data_1, n_digits = 0)

```


row
--------------------------------------------------

###{data-height=650}

```{r trends, show=FALSE}
colours <- c("purple",
             "magenta",
             "blue",
             "green",
             "graphite",
             "teal",
             "liberty",
             "rust")

colours <- phs_colours(sprintf("phs-%s", colours))

trend_data <- data %>%
  select(area, date_end, EASR) %>%
  arrange(area %in% big_areas, area) %>%
  rename(Area=area) %>% 
  pivot_wider(names_from = "Area", values_from = "EASR")

min_y <- trend_data %>% select(-date_end) %>% min()
max_y <- trend_data %>% select(-date_end) %>% max()
y_lower <- min_y - 0.1*(max_y-min_y)
y_upper <- max_y + 0.1*(max_y-min_y)

area_names <- trend_data %>% names() %>% tail(-1)
fig <- trend_data %>% 
  plot_ly(type = 'scatter', mode = 'lines',
          line=list(width=3.5)) %>% 
  layout(title = 'Trends in EASR',
         xaxis = list(title = 'Year ending'),
         yaxis = list (title = 'EASR (per 10,000)',
                       range = c(y_lower, y_upper)),
         hovermode = "x unified")


for (i in seq_along(area_names)){
  area <- area_names[[i]]
  trace_f <- as.formula(paste0("~`", area, "`"))
  if(area %in% big_areas){
    fig <- fig %>% add_trace(x=~date_end, y=trace_f, name=area, line=list(dash = 'dash', color=colours[[i]]))
  }else{
    fig <- fig %>% add_trace(x=~date_end, y=trace_f, name=area, line=list(color=colours[[i]]))  
  }

}
fig

```


Change Trends {data-icon="fa-table"}
===================================== 

Info {.sidebar}
-------------------------------------

**Alcohol-related hospital admissions**

**NHS Greater Glasgow and Clyde and HSCPs.**

- Percentage change in EASR (per 10,000 population) and Number of Admissions
- First table - % change from first year;  Second table - % change year-on-year
- The years are "rolling years" in that 30-Sep-2019 indicates the year from 30-Sep 2018 to 30-Sep-2019.
- In each table choose between the tabs to view % change in either EASR or Number of Admissions 
- Green cells indicate a decrease and red cells an increase. The darker the colour the bigger the change.
- A summary trend is shown at the end of each row of the table.
- If viewed on a narrow screen, press shift while scrolling on the mouse and hovering over the table to scroll the table horizontally.


row {.tabset}
--------------------------------------------------

### EASR - % change from first year

```{r reactable_4}
change_table_data_2 <- relative_change_table_data(data, "EASR")

table_with_sparklines(change_table_data_2, p_m_colouring = TRUE, sparkline_type="bar")
```

### Number - % change from first year

```{r reactable_3}
change_table_data_1 <- relative_change_table_data(data, "number")

table_with_sparklines(change_table_data_1, p_m_colouring = TRUE, sparkline_type="bar")
```


row {.tabset}
--------------------------------------------------

### EASR - % change year-on-year

```{r reactable_6}
change_table_data_4 <- year_on_year_change(data, "EASR")
table_with_sparklines(change_table_data_4, p_m_colouring = TRUE, sparkline_type="bar")
```

### Number - % change year-on-year

```{r reactable_5}
change_table_data_3 <- year_on_year_change(data, "number")
table_with_sparklines(change_table_data_3, p_m_colouring = TRUE, sparkline_type="bar")
```
